% mention that tf-idf features of this dataset are quite effective for both linear SVM and logistic regression, as evidenced by the high accuracy and macro-F1 scores on the test set (both around 0.91–0.92). However, as can be seen in the t-sne projections the classes are not perfectly separable, and have significant overlap in the center of the projection, which likely contributes to the misclassifications seen in the confusion matrices.

In this section, we discuss the results of our experiments and analyze the performance of both the Linear SVM and Logistic Regression models on the text classification task. We also explore potential reasons for the observed performance and suggest directions for future work.

It is evident from the results that both models perform quite well on the test set, with accuracies and macro-F1 scores above 0.90. This indicates that the TF-IDF features are effective for this classification task. However, the t-SNE projections of the test set predictions (Figures \ref{fig:linear_svm_test_prediction_map} and \ref{fig:logistic_regression_test_prediction_map}) reveal that the classes are not perfectly separable. The confusion matrices (Figures \ref{fig:linear_svm_test_confusion_matrix} and \ref{fig:logistic_regression_test_confusion_matrix}) show that there are some misclassifications, particularly between the `business' and `sci/tech' classes, which is also reflected in the t-SNE projections where the clusters for these classes overlap more than the others. Suggesting these categories share vocabulary that TF-IDF struggles to distinguish.

After our error analysis, we performed three ablation studies on the dev set to explore the impact of different feature extraction methods and preprocessing steps on model performance. We found that using both unigrams and bigrams together gave the best performance on the dev set, likely because it captures more contextual information than unigrams alone, while still being less sparse than bigrams alone. Additionally, we found that removing stopwords gave slightly better performance on the dev set (up to 62 fewer misclassifications for Logistic Regression), likely because it reduces noise in the data and focuses on more informative words. However, the differences in performance for both ablations were not very large, suggesting that while these choices can have an impact, they are not the primary drivers of model performance in this case.




% mention that perhaps non-linear models (e.g., kernel SVM, random forest, or neural networks) could potentially capture more complex relationships in the data and improve performance, but this would require further experimentation and tuning to confirm. And that we are still limited by the quality of the features (tf-idf), which might not capture all the nuances of the text data, and that exploring other feature extraction methods (e.g., word embeddings, n-grams) could also potentially improve performance.

% mention from the devlog:
% - unigram vs. bigram vs. unigram + bigram features: we found that using both unigrams and bigrams together gave the best performance on the dev set, likely because it captures more contextual information than unigrams alone, while still being less sparse than bigrams alone. However, the difference in performance was not very large, and it might be worth exploring other n-gram combinations (e.g., trigrams) or other feature extraction methods (e.g., word embeddings) in future work.
% - removing stopwords vs. not removing stopwords: we found that removing stopwords gave slightly better performance on the dev set, likely because it reduces noise in the data and focuses on more informative words. However, the difference in performance was not very large.
