Overall, the CNN performs slightly better than the LSTM across the full set of experiments, but the difference is small. The clearest gap appears at sequence length 64, where the CNN has about a 1 percentage point advantage in macro-F1. At sequence length 256, the gap is almost zero. This means that the CNN is stronger overall, but not by a large margin.

One important pattern is that the LSTM benefits more from longer input sequences. Its performance increases steadily from 64 to 256 tokens, while the CNN changes less across sequence lengths. A likely explanation is that the CNN can already extract useful local phrase patterns from shorter inputs, whereas the LSTM needs more context before its ability to model sequential information becomes fully useful. In other words, the CNN appears to be more effective on truncated inputs, while the LSTM catches up when it has access to longer sequences.

The class-wise results also support this picture. The CNN's advantage is strongest on the harder classes, especially Business and Sci/Tech, where local lexical patterns may be particularly informative. At the same time, the difference between the models becomes smaller at sequence length 256, and for some easier classes such as World and Sports the LSTM is competitive or slightly better. This suggests that the benefit of modelling longer context is class-dependent.

The learning curves indicate that the two models behave differently during training. The CNN shows relatively stable validation curves, while the LSTM shows stronger fluctuations later in training. This suggests that the LSTM is more prone to overfitting in this setup and may require more careful tuning or stronger regularisation. This is consistent with the hyperparameter results: the best CNN configuration changes only slightly across sequence lengths, while the LSTM best configuration changes more noticeably. In practice, this makes the CNN easier to tune and more robust across settings.

The development and test scores are very close for all runs, with gaps below roughly 0.005 macro-F1. This indicates that both models generalise well and that the model-selection procedure worked as intended. Even so, the practical conclusion of this assignment is that the CNN is the safer default choice for this task. It gives the best overall performance, is less sensitive to input truncation, and appears easier to tune. The LSTM can match the CNN more closely, but mainly when longer sequences and careful hyperparameter choices are used.
