This study has a few limitations. First, we only evaluate on AG News, so our conclusions may not transfer to datasets with different writing styles or label structures. A second limitation concerns tokenizer analysis: although the shared BPE tokenizer (vocab size 19{,}980, max vocab size 20{,}000) shows full coverage with zero OOV and a stable split rate of about 1.19 tokens per word, these coverage statistics do not guarantee that subword segmentation preserves all task-relevant distinctions. In particular, named entities and domain-specific terms may still be split into pieces that are harder for the models to use consistently.

Another important limitation is the tuning setup. Hyperparameter search was done with only 5 epochs per configuration, and we did not explicitly verify that this was long enough for strong and weak configurations to separate clearly. This means some settings may have looked worse simply because they learned more slowly, not because they were truly worse.

Regularisation is another place where our choices may have been too limited. In the best configurations, weight decay was either very small or zero, and the learning curves suggest that the LSTMs overfit slightly more than the CNNs. Because of this, it would have been useful to test higher weight decay values more aggressively, especially for the LSTM models.

Finally, we compare only CNN and LSTM models trained from scratch, so this is a comparison between two classical neural architectures rather than a comparison with the current strongest text-classification models. That does not affect the internal comparison in this report, but it does limit how far the absolute performance numbers can be taken.
